---
title: "UN Hackathon"
author: "ONS Health Surveillance"
date: "08/11/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include=FALSE}
library(leaflet)
library(tmap)
library(ggplot2)
library(cowplot)
library(viridis)
library(plotly)
library(readODS)
```

```{r read_data, include=FALSE}
ACLED_UK_clean <- read.csv("ACLED_UK_clean.csv", row.names = 1)
UK_sf <- rnaturalearth::ne_countries(scale = 50, country = "United Kingdom", returnclass = "sf") 

ACLED_UK_clean <- read.csv("ACLED_UK_clean.csv", row.names = 1)

#Convert dataframe into spatial object
ACLED_sf <- sf::st_as_sf(ACLED_UK_clean,
                         coords = c("longitude", "latitude"),
                         crs = "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")

Climate_protests <- ACLED_sf %>%
  dplyr::filter(.data$climate == "Y") %>%
  dplyr::select(.data$data_id,
                .data$action_group,
                .data$date,
                .data$sub_event_type,
                .data$notes)

distinct_protests <- Climate_protests %>%
  dplyr::group_by(data_id) %>%
  dplyr::slice(1) %>%
  dplyr::ungroup()
```

## Introduction
This report brings together information on different metrics for measuring the UK population’s perceptions of climate change, with the aim of providing a resource for policy makers to monitor the impact of climate change and associated policies on UK society.

## Methods

## Tools {.tabset}

### Where are protests happening?

```{r occurrence, echo=FALSE}

tmap::tmap_leaflet(
  tmap::tm_shape(distinct_protests) +
    tmap::tm_symbols(col = "sub_event_type",
                     size = 0.05,
                     clustering = F,
                     title.col="Protest type",
                     id = "Protest",
                     popup.vars = c("Protest by: " = "action_group",
                                    "Date: " = "date")) +
    tm_view(
    alpha = 0.8,
    symbol.size.fixed = TRUE
    )
  )  
```

### Which groups are growing membership?
```{r groups, echo=FALSE}
```
### opinion on climate from opn
```{r, echo = FALSE}

opn <- read.csv("OPN-data.csv")


## bar plots 
colnames(opn)[3] <- "All.Regions"
opn_long <- tidyr::gather(opn, region, percentage, All.Regions:South.West, factor_key=TRUE)

opn_long$region <- gsub("\\.", " ", opn_long$region)
colnames(opn_long)[1] <- "opinion"
opn_long$percentage <- as.numeric(opn_long$percentage)


# each table needs to be its own object 
table1 <- opn_long[opn_long$Table == "1",]
table2 <- opn_long[opn_long$Table == "2",]
table3 <- opn_long[opn_long$Table == "3",]
table4 <- opn_long[opn_long$Table == "4",]


ggplot(table1, aes(fill = opinion, y = percentage, x = region)) +
  geom_bar(position="stack", stat="identity") +
  theme_cowplot(16) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Percentage (%)", 
       x = "Region",
       fill = "") +
  scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 10)) +
  scale_fill_viridis_d(labels = function(x) stringr::str_wrap(x, width = 30)) +
  ggtitle("How positive or negative do you currently feel when \nyou think about the future of the environment?") +
  geom_vline(xintercept=1.5, linetype="dashed", lwd = 1) 


ggplot(table2, aes(fill = opinion, y = percentage, x = region)) +
  geom_bar(position="stack", stat="identity") +
  theme_cowplot(16) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Percentage (%)", 
       x = "Region",
       fill = "") +
  scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 10)) +
  scale_fill_viridis_d(labels = function(x) stringr::str_wrap(x, width = 30)) +
  ggtitle("How worried or unworried are you about the impact of climate change?") +
  geom_vline(xintercept=1.5, linetype="dashed", lwd = 1)


ggplot(table3, aes(fill = opinion, y = percentage, x = region)) +
  geom_bar(position="stack", stat="identity") +
  theme_cowplot(16) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Percentage (%)", 
       x = "Region",
       fill = "") +
  scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 10)) +
  scale_fill_viridis_d(labels = function(x) stringr::str_wrap(x, width = 30)) +
  ggtitle("Over the past month how anxious, if at all, \nhave you felt about the future of the environment?") +
  geom_vline(xintercept=1.5, linetype="dashed", lwd = 1)

ggplot(table4, aes(fill = opinion, y = percentage, x = region)) +
  geom_bar(position="stack", stat="identity") +
  theme_cowplot(16) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Number of votes", 
       x = "Region",
       fill = "") +
  scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 10)) +
  scale_fill_viridis_d(labels = function(x) stringr::str_wrap(x, width = 30)) +
  ggtitle("For what reasons have you not made any \nchanges to your lifestyle to tackle climate change?") +
  geom_vline(xintercept=1.5, linetype="dashed", lwd = 1) 
```
## References


### Public Support for Policies

```{r, echo = F}

beis_spreadsheet <- read.ods("BEIS_Data_Tables.ods")


### Policies ######## 

policies <- beis_spreadsheet[[14]] %>% 
  select(A, B, H)

#################### Format data ##########################################

### Generate all tables as list

## Each table is indexed in the same way, every 14 lines - so loop through to get these
table_seq <- seq(1, 71, by = 14) 

tables <- list()
iter <- 0

for (i in table_seq){
  
  iter <- iter + 1
  
  start <- i+4
  end <- i+9
  
  this_table <- policies[c(start:end),] %>% 
    select(support = B, perc = H) 
  
  this_table <- this_table %>% 
    mutate(support = factor(support, levels = unique(this_table$support)))
  
  tables[[iter]] <- this_table
  
}

### Create policy labels

category <- c("end to fuel car sales by 2035",
                "end to flight incentives",
                "frequent flier levy",
                "high emisssion product advertising bans",
                "citizens steering group for target monitoring",
                "emissions labelling on food/drink")

### Add category to each table to allow easier labelling in plotly

for(i in 1:6){
  
  tables[[i]] <- tables[[i]] %>% 
    mutate(cat = category[i]) ### add var for category
  
}


#### Create headline statement of support

support <- c()

### Get % that support policies overall
for(i in tables){
  
  perc_support <- sum(as.numeric(i[c(1, 2), 2])) ## take from top two rows of each columns
  perc_support <- round(100*perc_support, digits = 0)
  
  support <- c(support, perc_support)
}

## Make into a statement

statement <- c()

for(i in 1:length(tables)){
  
  this_statement <- paste0(support[i], "% support ", category[i])
  statement <- c(statement, this_statement)
  
}

statement2 <- stringr::str_wrap(statement, width = 15)

### Use red, amber, green colours
#my_colours <- c(RColorBrewer::brewer.pal(5, "Blues"), "#888888")
my_colours <- c("#2dc937", "#99c140", "#e7b416", "#db7b2b", "#cc3232")#, "#888888") ## use traffic light colour system
my_colours <- c(scales::muted(my_colours, l = 70, c = 90), "#888888") ## muting colours slightly


######################## Plot ###############################################

# Set grid coordinaetes for plots 
row <- c(0,0,0,
         1,1,1)
column <- c(0,1,2,
            0,1,2)

## Initiate plot_ly figure and set colours 

fig <- plot_ly(marker = list(colors = my_colours))

## set centres of each subplot
x_centres <- rep(c(2/13, 1/2, 11/13), 2) ## This was done through trial and error, may need to adjust in markdown
y_centres <- c(rep(5/6, 3), rep(1/6, 3))


### Create each subplot
for(i in c(1:6)){
  
  fig <- fig %>% add_pie(data = tables[[i]], labels = ~support, values = ~perc, 
                         name = category[i],
                         textinfo = "none",
                         hoverinfo = "text",
                         text = ~ paste0(
                           '</br>', cat, 
                           '</br>', support, ": ", round(100*as.numeric(perc), 1), "%"),
                         domain = list(row = row[i], column = column[i]), hole = 0.6,
                         direction = "clockwise",
                         sort = FALSE) %>%
    add_annotations(x = x_centres[i],
                    y = y_centres[i],
                    text = statement2[i],
                    xref = "paper",
                    yref = "paper",
                    xanchor = "center",
                    yanchor = "center",
                    showarrow = FALSE)
    #layout(annotations = list(text = statement[i]))
}

## Format
fig <- fig %>% layout(title = "Public Support of Climate Policies", showlegend = T,
                      grid=list(rows=2, columns=3),
                      xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                      yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                      legend = list(orientation = "h",
                                    xanchor = "center",
                                    x = 0.5))



## Final figure
fig


```
## References
