---
title: "UN Hackathon"
author: "ONS Health Surveillance"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    df_print: paged
    toc: true
    toc_depth: 6
    number_sections: false
    toc_float: true
    code_folding: hide
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

```{r libraries, include=FALSE}
library(leaflet)
library(tmap)
library(ggplot2)
library(cowplot)
library(viridis)
library(plotly)
library(readODS)
library(stringr)
library(dplyr)
library(haven)
```

```{r read_data, include=FALSE}
ACLED_UK_clean <- read.csv("ACLED_UK_clean.csv", row.names = 1)
UK_sf <- rnaturalearth::ne_countries(scale = 50, country = "United Kingdom", returnclass = "sf") 

ACLED_UK_clean <- read.csv("ACLED_UK_clean.csv", row.names = 1)

#Convert dataframe into spatial object
ACLED_sf <- sf::st_as_sf(ACLED_UK_clean,
                         coords = c("longitude", "latitude"),
                         crs = "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")

Climate_protests <- ACLED_sf %>%
  dplyr::filter(.data$climate == "Y") %>%
  dplyr::select(.data$data_id,
                .data$action_group,
                .data$date,
                .data$sub_event_type,
                .data$notes)

distinct_protests <- Climate_protests %>%
  dplyr::group_by(data_id) %>%
  dplyr::slice(1) %>%
  dplyr::ungroup()
```

# Introduction
This report brings together information on different metrics for measuring the UK population’s perceptions of climate change, with the aim of providing a resource for policy makers to monitor the impact of climate change and associated policies on UK society.

# Methods

# Tools {.tabset}

## Where are protests happening?

```{r occurrence, echo=FALSE}

tmap::tmap_leaflet(
  tmap::tm_shape(distinct_protests) +
    tmap::tm_symbols(col = "sub_event_type",
                     size = 0.05,
                     clustering = F,
                     title.col="Protest type",
                     id = "Protest",
                     popup.vars = c("Protest by: " = "action_group",
                                    "Date: " = "date")) +
    tm_view(
    alpha = 0.8,
    symbol.size.fixed = TRUE
    )
  )  
```

## Which groups are growing membership?
```{r groups, echo=FALSE}
twitter_data <- read.csv("tidy_twitter_data.csv")
twitter_data[,2:36] <- as.data.frame(sapply(twitter_data[,2:36], as.numeric))
                                  
twitter_data <- tidyr::pivot_longer(twitter_data, 2:36, names_to = "Date")

twitter_data$Date <- lubridate::my(twitter_data$Date)
twitter_data <- dplyr::rename(twitter_data, `Protest group` = `ï..Twitter.Handle`) 

trends <- ggplot(twitter_data) +
  geom_line(aes(x = Date, y = log10(value), colour = `Protest group`))

plotly::ggplotly(trends)

```

## Which groups are searched for on google?
```{r gtrends, echo = F}
interest_over_time <- readr::read_csv("gtrends_interest_over_time.csv")
a <- ggplot(interest_over_time)+
  geom_line(aes(x = date, y = as.numeric(hits), colour = keyword))

b <-  plotly::ggplotly(a)

b

```

## {-}

# Opinion on climate from OPN {.tabset}

## Plot 1
```{r, echo = FALSE}

opn <- read.csv("OPN-data.csv")


## bar plots 
colnames(opn)[3] <- "All.Regions"
opn_long <- tidyr::gather(opn, region, percentage, All.Regions:South.West, factor_key=TRUE)

opn_long$region <- gsub("\\.", " ", opn_long$region)
colnames(opn_long)[1] <- "opinion"
opn_long$percentage <- as.numeric(opn_long$percentage)


# each table needs to be its own object 
table1 <- opn_long[opn_long$Table == "1",]
table2 <- opn_long[opn_long$Table == "2",]
table3 <- opn_long[opn_long$Table == "3",]
table4 <- opn_long[opn_long$Table == "4",]


ggplot(table1, aes(fill = opinion, y = percentage, x = region)) +
  geom_bar(position="stack", stat="identity") +
  theme_cowplot(12) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Percentage (%)", 
       x = "Region",
       fill = "") +
  scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 10)) +
  scale_fill_viridis_d(labels = function(x) stringr::str_wrap(x, width = 30)) +
  ggtitle("How positive or negative do you currently feel when \nyou think about the future of the environment?") +
  geom_vline(xintercept=1.5, linetype="dashed", lwd = 1) 

```

## Plot 2
```{r}

ggplot(table2, aes(fill = opinion, y = percentage, x = region)) +
  geom_bar(position="stack", stat="identity") +
  theme_cowplot(12) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Percentage (%)", 
       x = "Region",
       fill = "") +
  scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 10)) +
  scale_fill_viridis_d(labels = function(x) stringr::str_wrap(x, width = 30)) +
  ggtitle("How worried or unworried are you about the impact \nof climate change?") +
  geom_vline(xintercept=1.5, linetype="dashed", lwd = 1)

```


## Plot 3
```{r}


ggplot(table3, aes(fill = opinion, y = percentage, x = region)) +
  geom_bar(position="stack", stat="identity") +
  theme_cowplot(12) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "Percentage (%)", 
       x = "Region",
       fill = "") +
  scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 10)) +
  scale_fill_viridis_d(labels = function(x) stringr::str_wrap(x, width = 30)) +
  ggtitle("Over the past month how anxious, if at all, \nhave you felt about the future of the environment?") +
  geom_vline(xintercept=1.5, linetype="dashed", lwd = 1)

```

## Plot 4
```{r, fig.width=7, fig.height=15}
ggplot(table4, aes(fill = opinion, y = percentage, x = region)) +
  geom_bar(position="stack", stat="identity") +
  theme_cowplot(12) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.position = "none") +
  labs(y = "Percentage (%)", 
       x = "Region",
       fill = "") +
  scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 10)) +
  scale_fill_viridis_d(labels = function(x) stringr::str_wrap(x, width = 30)) +
  ggtitle("For what reasons have you not made any \nchanges to your lifestyle to tackle climate change?") +
  geom_vline(xintercept=1.5, linetype="dashed", lwd = 1) +
  facet_wrap(~opinion, ncol = 1)
```

## {-}

# Public Perception of climate change threat 

## Overall

```{r}
LRP_UK <- read.csv("LRP_UK_clean.csv")

#### Overall figures of concerns

LRP_UK <- LRP_UK %>% 
  mutate(
    threat_percieved = case_when(Q3 == 1 ~ "Very serious",
                                 Q3 == 2 ~ "Somewhat serious",
                                 Q3 == 3 ~ "Not a threat at all",
                                 Q3 == 98 ~ "Don't know")
  )


threat_props <- LRP_UK %>% 
  filter(!is.na(threat_percieved)) %>% 
  group_by(Year) %>% 
  count(threat_percieved) %>% 
  mutate(perc = 100*n/sum(n))


my_colours <- c("#99c140", "#e7b416", "#cc3232", "#888888") ## use traffic light colour system
#my_colours <- c(scales::muted(my_colours, l = 70, c = 90), "#888888")


fig <- plot_ly(threat_props, 
               x = ~perc, 
               y = ~Year, 
               color = ~threat_percieved,
               name = ~threat_percieved,
               type = "bar",
               orientation = "h",
               colors = rev(my_colours),
               hoverinfo = "text",
               text = ~ paste0(
                 '</br>', threat_percieved, ":", 
                 '</br>', round(perc, 1), "%")) %>% 
  layout(
    title = "Perception of Climate Change Threat to Country in the Next 20 Years",
    barmode = "stack",
    xaxis = list(title = FALSE),
    yaxis = list(showgrid = FALSE, zeroline = FALSE, title = FALSE, tickvals = c(2019, 2021)),
    legend = list(orientation = "h",
    xanchor = "center",
    x = 0.5))

fig



```


## Effect of demographics on perceptions

```{r}

### Logistic regression looking at predictors of percieveing climate change as a risk to country

## Set level orders/reference categories

LRP_UK <- LRP_UK %>% 
  mutate(AgeGroup = factor(AgeGroup, levels = c("15_29", "30_49", "50_64", "65_94")),
         education_level = factor(education_level, levels = c("Low", "Medium", "High")),
         Income_categories = factor(Income_categories, levels = c("Poorest 20%",
                                                                  "Second 20%",
                                                                  "Third 20%",
                                                                  "Fourth 20%",
                                                                  "Richest 20%")),
         Year = as.character(Year),
         Year = factor(Year, levels = c("2019", "2021")),
         Gender = as_factor(Gender),
         Urbanicity = as_factor(Urbanicity),
         HouseholdSize = factor(HouseholdSize, levels = c("1_2", "3_4", "5+")),
         ChildrenInHousehold = factor(ChildrenInHousehold, levels = c("No", "Yes")))


## Define model
my_model <- "climate_threat ~ AgeGroup + Gender + education_level + Income_categories + Urbanicity + HouseholdSize + ChildrenInHousehold + Year"

## Run model
threat.mod <- glm(my_model,
                  data = LRP_UK,
                  family = "binomial")



### Get ORs and CIs

threat_ORS <- exp(cbind(coef(threat.mod), confint.default(threat.mod)))


threat_ORS_fin <- data.frame(
  level = rownames(threat_ORS),
  OR = threat_ORS[,1],
  ll = threat_ORS[,2],
  ul = threat_ORS[,3],
  p = coef(summary(threat.mod))[, 4]
)


## Define variable info for plot

vars <- c("AgeGroup", "Gender", "education_level", "Income_categories", 
          "Urbanicity", "HouseholdSize", "ChildrenInHousehold", "Year")

refs <- c("AgeGroup15_29", "GenderFemale", "education_levelLow",
          "Income_categoriesPoorest 20%", "UrbanicityRural",
          "HouseholdSize1_2", "ChildrenInHouseholdsNo", "Year2019")

reference_categories <- data.frame(
  level = c("AgeGroup15_29", "GenderFemale", "education_levelLow",
            "Income_categoriesPoorest 20%", "UrbanicityRural",
            "HouseholdSize1_2", "ChildrenInHouseholdNo", "Year2019"),
  OR = 1
)


## seperate variables and levels and set level orders
threat_plot_data <- bind_rows(reference_categories, threat_ORS_fin) %>% 
  mutate(variable = str_extract(level, paste(vars, collapse = "|")),
         lev = str_remove_all(level, paste(vars, collapse = "|"))) %>% 
  filter(!is.na(variable))

level_ord <- c()

for(i in vars){
  
  lev <- levels(LRP_UK[, i])
  level_ord <- c(level_ord, lev)
}


threat_plot_data <- threat_plot_data %>% 
  mutate(lev = factor(lev, levels = level_ord)) %>% 
  arrange(lev)


### Plot

ggplot(threat_plot_data, aes(x = OR, y = lev, colour = variable)) +
  geom_point(size = 2) +
  scale_x_log10() +
  scale_color_brewer(palette = "Set2") +
  geom_errorbar(aes(xmin = ll, xmax = ul), width = 0.5) +
  geom_vline(xintercept = 1, colour = "black", linetype = "dashed") +
  labs(title = "How Climate Change Threat Perception Varies by Demographic in the UK") +
  theme_classic() +
  theme(axis.line.x = element_blank(), panel.grid.major.x = element_line(colour = "grey90", linetype = "dashed"), axis.ticks.x = element_blank(),
        legend.position = "none", strip.text.y = element_text(size = 7, angle = 0)) +
  ylab(NULL) +
  xlab("Odds Ratio") +
  facet_grid(rows = vars(variable), scales = "free", space = "free")



```




# Public Support for Policy and personal changes {.tabset}

## Policies 

```{r, echo = F}

beis_spreadsheet <- read.ods("BEIS_Data_Tables.ods")


### Policies ######## 

policies <- beis_spreadsheet[[14]] %>% 
  select(A, B, H)

#################### Format data ##########################################

### Generate all tables as list

## Each table is indexed in the same way, every 14 lines - so loop through to get these
table_seq <- seq(1, 71, by = 14) 

tables <- list()
iter <- 0

for (i in table_seq){
  
  iter <- iter + 1
  
  start <- i+4
  end <- i+9
  
  this_table <- policies[c(start:end),] %>% 
    select(support = B, perc = H) 
  
  this_table <- this_table %>% 
    mutate(support = factor(support, levels = unique(this_table$support)))
  
  tables[[iter]] <- this_table
  
}

### Create policy labels

category <- c("end to fuel car sales by 2035",
                "end to flight incentives",
                "frequent flier levy",
                "high emisssion product advertising bans",
                "citizens steering group for target monitoring",
                "emissions labelling on food/drink")

### Add category to each table to allow easier labelling in plotly

for(i in 1:6){
  
  tables[[i]] <- tables[[i]] %>% 
    mutate(cat = category[i]) ### add var for category
  
}


#### Create headline statement of support

support <- c()

### Get % that support policies overall
for(i in tables){
  
  perc_support <- sum(as.numeric(i[c(1, 2), 2])) ## take from top two rows of each columns
  perc_support <- round(100*perc_support, digits = 0)
  
  support <- c(support, perc_support)
}

## Make into a statement

statement <- c()

for(i in 1:length(tables)){
  
  this_statement <- paste0(support[i], "% support ", category[i])
  statement <- c(statement, this_statement)
  
}

statement2 <- stringr::str_wrap(statement, width = 15)

### Use red, amber, green colours
#my_colours <- c(RColorBrewer::brewer.pal(5, "Blues"), "#888888")
my_colours <- c("#2dc937", "#99c140", "#e7b416", "#db7b2b", "#cc3232")#, "#888888") ## use traffic light colour system
my_colours <- c(scales::muted(my_colours, l = 70, c = 90), "#888888") ## muting colours slightly


######################## Plot ###############################################

# Set grid coordinaetes for plots 
row <- c(0,0,0,
         1,1,1)
column <- c(0,1,2,
            0,1,2)

## Initiate plot_ly figure and set colours 

fig <- plot_ly(marker = list(colors = my_colours))

## set centres of each subplot
x_centres <- rep(c(2/13, 1/2, 11/13), 2) ## This was done through trial and error, may need to adjust in markdown
y_centres <- c(rep(5/6, 3), rep(2/15, 3))


### Create each subplot
for(i in c(1:6)){
  
  fig <- fig %>% add_pie(data = tables[[i]], labels = ~support, values = ~perc, 
                         name = category[i],
                         textinfo = "none",
                         hoverinfo = "text",
                         text = ~ paste0(
                           '</br>', cat, 
                           '</br>', support, ": ", round(100*as.numeric(perc), 1), "%"),
                         domain = list(row = row[i], column = column[i]), hole = 0.6,
                         direction = "clockwise",
                         sort = FALSE) %>%
    add_annotations(x = x_centres[i],
                    y = y_centres[i],
                    text = statement2[i],
                    xref = "paper",
                    yref = "paper",
                    xanchor = "center",
                    yanchor = "center",
                    showarrow = FALSE,
                    textfont = list(family = "sans serif", size = 12))
    #layout(annotations = list(text = statement[i]))
}

## Format
fig <- fig %>% layout(title = "Public Support of Climate Policies", showlegend = T,
                      grid=list(rows=2, columns=3),
                      xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                      yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                      legend = list(orientation = "h",
                                    xanchor = "center",
                                    x = 0.5))



## Final figure
fig


```


## Personal changes 1

```{r}
### actions ######## 

actions <- beis_spreadsheet[[10]] %>% 
  select(A, B, H)

#################### Format data ##########################################

### Generate all tables as list

## Each table is indexed in the same way, every 15 lines - so loop through to get these (Do top 4 seperately as in different format)
table_seq <- seq(1, 46, by = 15) 

tables <- list()
iter <- 0

for (i in table_seq){
  
  iter <- iter + 1
  
  start <- i+4
  end <- i+10
  
  this_table <- actions[c(start:end),] %>% 
    select(support = B, perc = H) 
  
  this_table <- this_table %>% 
    mutate(support = factor(support, levels = unique(this_table$support)))
  
  tables[[iter]] <- this_table
  
}


### Create policy labels

category <- c("use a green energy supplier",
              "use a smart meter",
              "eat mainly plant-based meals",
              "minimise food waste")

### Add category to each table to allow easier labelling in plotly

for(i in 1:4){
  
  tables[[i]] <- tables[[i]] %>% 
    mutate(cat = category[i]) ### add var for category
  
}


#### Create headline statement of support

support <- c()

### Get % that support actions overall
for(i in tables){
  
  perc_support <- sum(as.numeric(i[c(1:3), 2])) ## take from top two rows of each columns
  perc_support <- round(100*perc_support, digits = 0)
  
  support <- c(support, perc_support)
}

## Make into a statement

statement <- c()

for(i in 1:length(tables)){
  
  this_statement <- paste0(support[i], "% at least 'somewhat likely' to ", category[i])
  statement <- c(statement, this_statement)
  
}

statement2 <- str_wrap(statement, width = 15)

### Use red, amber, green colours
#my_colours <- c(RColorBrewer::brewer.pal(5, "Blues"), "#888888")
my_colours <- c("#2dc937", "#99c140", "#e7b416", "#db7b2b", "#cc3232")#, "#888888") ## use traffic light colour system
my_colours <- c("#238b45", scales::muted(my_colours, l = 70, c = 90), "#888888") ## muting colours slightly


######################## Plot ###############################################

# Set grid coordinaetes for plots 
row <- c(0,0,
         1,1)
column <- c(0,1,
            0,1)



## Initiate plot_ly figure and set colours 

fig <- plot_ly(marker = list(colors = my_colours))

## set centres of each subplot
x_centres <- rep(c(2.1/9, 6.9/9), 2) ## This was done through trial and error, may need to adjust in markdown
y_centres <- c(rep(5/6, 2), rep(1/6, 2))


### Create each subplot
for(i in c(1:4)){
  
  fig <- fig %>% add_pie(data = tables[[i]], labels = ~support, values = ~perc, 
                         name = category[i],
                         textinfo = "none",
                         hoverinfo = "text",
                         text = ~ paste0(
                           '</br>', cat, 
                           '</br>', support, ": ", round(100*as.numeric(perc), 1), "%"),
                         domain = list(row = row[i], column = column[i]), hole = 0.6,
                         direction = "clockwise",
                         sort = FALSE) %>%
    add_annotations(x = x_centres[i],
                    y = y_centres[i],
                    text = statement2[i],
                    xref = "paper",
                    yref = "paper",
                    xanchor = "center",
                    yanchor = "center",
                    showarrow = FALSE)
  #layout(annotations = list(text = statement[i]))
}

## Format
fig <- fig %>% layout(title = "Liklihood of making changes in the next 6 months", showlegend = T,
                      grid=list(rows=2, columns=2),
                      xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                      yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                      legend = list(orientation = "h",
                                    xanchor = "center",
                                    x = 0.5))



## Final figure
fig

```

## Personal changes 2

```{r}

#### Repeating for actions now


## Each table is indexed in the same way, every 15 lines - so loop through to get these (Do top 4 seperately as in different format)
table_seq <- seq(1, 15, by = 14) 

tables <- list()
iter <- 0

for (i in table_seq){
  
  iter <- iter + 1
  
  start <- i+64
  end <- i+69
  
  this_table <- actions[c(start:end),] %>% 
    select(support = B, perc = H) 
  
  this_table <- this_table %>% 
    mutate(support = factor(support, levels = unique(this_table$support)))
  
  tables[[iter]] <- this_table
  
}


### Create policy labels

category <- c("use less heating",
              "reduce thermostat temperature")

### Add category to each table to allow easier labelling in plotly

for(i in 1:2){
  
  tables[[i]] <- tables[[i]] %>% 
    mutate(cat = category[i]) ### add var for category
  
}


#### Create headline statement of support

support <- c()

### Get % that support actions overall
for(i in tables){
  
  perc_support <- sum(as.numeric(i[c(1, 2), 2])) ## take from top two rows of each columns
  perc_support <- round(100*perc_support, digits = 0)
  
  support <- c(support, perc_support)
}

## Make into a statement

statement <- c()

for(i in 1:length(tables)){
  
  this_statement <- paste0(support[i], "% at least 'somewhat likely' to ", category[i])
  statement <- c(statement, this_statement)
  
}

statement2 <- str_wrap(statement, width = 15)

### Use red, amber, green colours
#my_colours <- c(RColorBrewer::brewer.pal(5, "Blues"), "#888888")
my_colours <- c("#2dc937", "#99c140", "#e7b416", "#db7b2b", "#cc3232")#, "#888888") ## use traffic light colour system
my_colours <- c(scales::muted(my_colours, l = 70, c = 90), "#888888") ## muting colours slightly


######################## Plot ###############################################

# Set grid coordinaetes for plots 
row <- c(0,0)
column <- c(0,1)






## Initiate plot_ly figure and set colours 

fig <- plot_ly(marker = list(colors = my_colours))

## set centres of each subplot
x_centres <- rep(c(2.1/9, 6.9/9)) ## This was done through trial and error, may need to adjust in markdown
#y_centres <- c(rep(5/6, 2), rep(1/6, 2))


### Create each subplot
for(i in c(1:2)){
  
  fig <- fig %>% add_pie(data = tables[[i]], labels = ~support, values = ~perc, 
                         name = category[i],
                         textinfo = "none",
                         hoverinfo = "text",
                         text = ~ paste0(
                           '</br>', cat, 
                           '</br>', support, ": ", round(100*as.numeric(perc), 1), "%"),
                         domain = list(row = row[i], column = column[i]), hole = 0.6,
                         direction = "clockwise",
                         sort = FALSE) %>%
    add_annotations(x = x_centres[i],
                    y = 0.5,
                    text = statement2[i],
                    xref = "paper",
                    yref = "paper",
                    xanchor = "center",
                    yanchor = "center",
                    showarrow = FALSE)
  #layout(annotations = list(text = statement[i]))
}

## Format
fig <- fig %>% layout(title = "Liklihood of making changes compared to last winter", showlegend = T,
                      grid=list(rows=1, columns=2),
                      xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                      yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                      legend = list(orientation = "h",
                                    xanchor = "center",
                                    x = 0.5))



## Final figure
fig

```

## Personal changes 3

```{r}

table_seq <- seq(1, 31, by = 15) 

tables <- list()
iter <- 0

for (i in table_seq){
  
  iter <- iter + 1
  
  start <- i+92
  end <- i+98
  
  this_table <- actions[c(start:end),] %>% 
    select(support = B, perc = H) 
  
  this_table <- this_table %>% 
    mutate(support = factor(support, levels = unique(this_table$support)))
  
  tables[[iter]] <- this_table
  
}


### Create policy labels

category <- c("buy an electric car (instead of petrol/diesel)",
              "avoid travelling by plane",
              "switch to low-carbon heating technology")

### Add category to each table to allow easier labelling in plotly

for(i in 1:3){
  
  tables[[i]] <- tables[[i]] %>% 
    mutate(cat = category[i]) ### add var for category
  
}


#### Create headline statement of support

support <- c()

### Get % that support actions overall
for(i in tables){
  
  perc_support <- sum(as.numeric(i[c(1:3), 2])) ## take from top two rows of each columns
  perc_support <- round(100*perc_support, digits = 0)
  
  support <- c(support, perc_support)
}

## Make into a statement

statement <- c()

for(i in 1:length(tables)){
  
  this_statement <- paste0(support[i], "% at least 'somewhat likely' to ", category[i])
  statement <- c(statement, this_statement)
  
}

statement2 <- str_wrap(statement, width = 15)

### Use red, amber, green colours
#my_colours <- c(RColorBrewer::brewer.pal(5, "Blues"), "#888888")
my_colours <- c("#2dc937", "#99c140", "#e7b416", "#db7b2b", "#cc3232")#, "#888888") ## use traffic light colour system
my_colours <- c("#238b45", scales::muted(my_colours, l = 70, c = 90), "#888888") ## muting colours slightly


######################## Plot ###############################################

# Set grid coordinaetes for plots 
row <- c(0,0, 0)
column <- c(0,1,2)



## Initiate plot_ly figure and set colours 

fig <- plot_ly(marker = list(colors = my_colours))

## set centres of each subplot
x_centres <- c(2/13, 1/2, 11/13) ## This was done through trial and error, may need to adjust in markdown
y_centres <- 0.5


### Create each subplot
for(i in c(1:3)){
  
  fig <- fig %>% add_pie(data = tables[[i]], labels = ~support, values = ~perc, 
                         name = category[i],
                         textinfo = "none",
                         hoverinfo = "text",
                         text = ~ paste0(
                           '</br>', cat, 
                           '</br>', support, ": ", round(100*as.numeric(perc), 1), "%"),
                         domain = list(row = row[i], column = column[i]), hole = 0.6,
                         direction = "clockwise",
                         sort = FALSE) %>%
    add_annotations(x = x_centres[i],
                    y = y_centres[i],
                    text = statement2[i],
                    xref = "paper",
                    yref = "paper",
                    xanchor = "center",
                    yanchor = "center",
                    showarrow = FALSE)
  #layout(annotations = list(text = statement[i]))
}

## Format
fig <- fig %>% layout(title = "Liklihood of making changes next time", showlegend = T,
                      grid=list(rows=1, columns=3),
                      xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                      yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                      legend = list(orientation = "h",
                                    xanchor = "center",
                                    x = 0.5))



## Final figure
fig

```

## {-}


# References
